---
title: "Initial Korean covid 19"
author: "Shawn Olson"
date: "10/7/24"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?






## Graphical results - use ggplot commands to do this  


```{r}
barchartGC(~result + Sex,data=kRdata)
barchartGC(~result + Sex,data=kRdata, type="percent")

```
  





  
  Most of the people alive were female, making up about 55%, while males were around 45%. But when it came to those who died, about 65% were male and 45% were female. This shows that more males died compared to females, with males making up a much larger part of the deaths, almost twice as many as females.
  
  
## Numerical results

```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```

The data shows that more women than men are alive, with about 56% being female and 44% male. But when it comes to those who have died, more men than women have passed away—about 64% were men and 36% were women. In total, 3% of men have died, compared to just 1.4% of women. This means that the number of men who have died is more than double the number of women.

## Inferential results 




## Conclusions

